Negative Selection in the 20th Century

### 2020-06-18 why-negative-selection.Rmd
Add census weighting and use in paper. Rework _drake to use "static branching".

standard_ggplot <- function (
        dfr, 
        fill_col, 
        n_regs, 
        ...,
        score_col = quo(term), 
        order_idx = 1, 
        n_cats    = NULL
      ) {
  if (! missing(score_col)) score_col <- enquo(score_col)
  fill_col <- if (! missing(fill_col)) enquo(fill_col) else quo(NULL)
  if (missing(n_cats)) {
    n_cats <- if (missing(fill_col)) 1 else length(unique(pull(dfr, 
                {{fill_col}})))
  }

@@

* If we weight with the GHS, and plot the means of figure 1 using this w
  weighting, most things stay the same - but the change in EA is reversed! EA
  increases over time. Could this be because the sample includes many
  relatively educated older people? If so, then mean effects are *overestimated*
  by figure 1. 
* Need to make the weighting very watertight. 
  - Include income? 
  - Interact age and other variables?
  - Investigate "MRP" (Gelman 2005)
  - Understand reweighting on subsets of survey data.
  - Check for existing work
  - Chris Hanretty suggested using 2011 census. Household size/type would also
    be good.
* Reweight other regressions (e.g. the omnibus regression in the appendix)
* Could be useful: f.2139 - age first had sex (includes "never had sex" 
  which may explain some of the many NAs for f.2141, num sex partners)
*  Need f.6138 to correctly calculate `age_fulltime_edu` including
  those who went to college.
* Look at geography, esp. in siblings regressions.
* control for age in n_partners regressions.

@@

drake::loadd(res_weighted)
drake::loadd(res_sibs_parent_weights)
drake::loadd(res_all)
res_weighted_all <- bind_rows(
        "N children" = res_weighted, 
        "N siblings" = res_sibs_parent_weights, 
      .id = "dep.var") 
res_weighted_all$reg.type <- "weighted"
res_weighted_all <- bind_rows(
        res_weighted_all,
        res_all %>% filter(reg.type == "raw") %>% select(-score_name)
      )

res_wide <- full_join(
        res_weighted,
        res_sibs_parent_weights,
        by = "term",
        suffix = c(".children", ".sibs")
      ) %>% 
      filter(p.value.children < 0.05/33 | p.value.sibs < 0.05/33)

@@

To compensate for ascertainment bias in the UK Biobank sample, we weight participants
by sex, age (within the 40-71 age group), and education. Our sample weights are
calibrated based on the 2006 General Household Survey. We then calculate the 
proportions of respondents within each sibling group size, based on the respondent
weights, and use this to create weights for the sibling regressions.

@@

@@

drake::loadd(res_flb_weights)
drake::loadd(res_sex)
res_flb_all <- left_join(
        res_flb_weights, 
        res_sex %>% filter(sex=="Female") %>% select(-subset, -sex), 
        by = "term", 
        suffix = c(".wt", ".nowt")
      ) %>% 
      mutate(prop_estimate = estimate.wt/estimate.nowt)

@@

bind_rows(
        Weighted   = res_flb_weights, 
        Unweighted = res_sex %>% filter(sex == "Female") %>% select(-subset, -sex),
        .id        = "Regression"
      ) %>% 
      standard_ggplot(Regression, n_regs = 66)
```

>>>>

standard_ggplot <- function (
        dfr, 
        fill_col, 
        n_regs, 
        ...,
        score_col = quo(term), 
        order_idx = 1, 
        n_cats    = NULL
      ) {
  if (! missing(score_col)) score_col <- enquo(score_col)
  mfc <- missing(fill_col)
  fill_col <- if (mfc) quo(NULL) else enquo(fill_col)
  if (missing(n_cats)) {
    n_cats <- if (mfc) 1 else length(unique(pull(dfr, {{fill_col}})))
  }

@@

* If we weight with the GHS, and plot the means of figure 1 using this w
  weighting, most things stay the same - but the change in EA is reversed! EA
  increases over time. Could this be because the sample includes many
  relatively educated older people? If so, then mean effects are *overestimated*
  by figure 1. 
* Reweight other regressions (e.g. the omnibus regression in the appendix)
* Could be useful: f.2139 - age first had sex (includes "never had sex" 
  which may explain some of the many NAs for f.2141, num sex partners)
* Look at geography, esp. in siblings regressions.
* control for age in n_partners regressions.

@@

drake::loadd(res_wt_ghs_weights)
drake::loadd(res_wt_flb_weights)
drake::loadd(res_wt_msoa_weights)
drake::loadd(res_wt_age_qual_weights)
drake::loadd(res_sibs_parent_weights)
drake::loadd(res_all)

res_wt_combined <- bind_rows(
  None                     = res_all %>% 
                               filter(reg.type == "raw", dep.var == "N children") %>% 
                               select(-reg.type, -dep.var, -score_name),
  Geographical             = res_wt_msoa_weights,
  `Age/Qualification`      = res_wt_age_qual_weights,
  `Age/Qual/FLB`  = res_wt_flb_weights,
  .id = "Weights"
)

res_wt_cb_wide <- res_wt_combined %>% 
                    tidyr::pivot_wider(
                      id_cols     = term,
                      names_from  = Weights,
                      values_from = estimate
                    ) %>% 
                    rowwise() %>% 
                    mutate(
                      consistent = all(c_across(-term) > 0) ||
                        all(c_across(-term) < 0)
                    ) %>% 
                    ungroup() %>% 
                    left_join(
                      res_wt_combined %>% 
                        filter(Weights == "None") %>% 
                        select(term, p.value)
                    )

rel_sizes <- res_wt_cb_wide %>% 
                filter(
                  consistent, 
                  p.value < 0.05/length(score_names)
                ) %>% 
                mutate(
                  across(Geographical:`Age/Qual/FLB`, ~ .x/None)
                ) %>% 
                select(- consistent, - None, - p.value) %>% 
                mutate(
                  term = pretty_names(term)
                )

rel_sizes_summary <- rel_sizes %>% 
                summarize(
                  across(Geographical:`Age/Qual/FLB`, ~ c(mean(.x), median(.x)))
                ) %>% 
                mutate(
                  term = c("Mean", "Median")
                )

# TODO: move later
res_weighted_all <- bind_rows(
        "N children" = res_wt_ghs_weights, 
        "N siblings" = res_sibs_parent_weights, 
      .id = "dep.var") 
res_weighted_all$reg.type <- "weighted"
res_weighted_all <- bind_rows(
        res_weighted_all,
        res_all %>% filter(reg.type == "raw") %>% select(-score_name)
      )

res_wide <- full_join(
        res_wt_ghs_weights,
        res_sibs_parent_weights,
        by = "term",
        suffix = c(".children", ".sibs")
      ) %>% 
      filter(p.value.children < 0.05/33 | p.value.sibs < 0.05/33)

@@

To compensate for ascertainment bias in the UK Biobank sample, we weight 
participants using data from the 2011 Census and from the 2006 General Household
Survey (GHS). We try three alternative weighting schemes:

* Geographical weighting by census MSOA, age and presence/absence of a partner;
* Weighting by age and highest educational qualification;
* Weighting by age, highest qualification, and age at first live birth, using
  GHS data.

Figure \@ref(fig:plot-res-wt) shows the results. Effect sizes are significantly
larger in absolute value. Table \@ref(tab:tbl-res-wt) gives effect sizes as a 
proportion of unweighted effect sizes.

```{r tbl-res-wt}
rel_sizes %>% 
      arrange(desc(`Age/Qual/FLB`)) %>% 
      bind_rows(rel_sizes_summary) %>% 
      rename(PGS = term) %>% 
      as_hux() %>% 
      set_caption(
        "Weighted effect sizes as a proportion of unweighted"
      ) %>% 
      insert_row("", "Weighting", fill = "") %>% 
      merge_cells(1, 2:4) %>% 
      set_align(1, 2, "centre") %>% 
      set_header_rows(1, TRUE) %>% 
      theme_compact() %>% 
      style_headers(bold = TRUE) %>% 
      set_bottom_border(1, 2:4) %>% 
      set_bottom_border(2, everywhere) %>% 
      set_background_color(final(2), everywhere, "grey80") %>% 
      add_footnote(
        "Only consistent and significant (when unweighted) estimates are shown",
        font_size   = 8, 
        top_padding = 2
      )

```{r plot-res-wt, fig.cap = "Effects of polygenic scores on fertility. Weighted regressions."}

res_wt_combined %>% 
  mutate(
    Weights  = fct_relevel(Weights, "Geographical", "Age/Qualification",
                "Age/Qual/FLB", "None"),
    term     = pretty_names(term),
    term     = fct_reorder(term, estimate, order_abs(4))
  ) %>% 
  ggplot(aes(x = estimate, y = term, shape = Weights, colour = Weights)) +
  geom_point(size = 2) +
  my_vline +
  scale_colour_manual(values = c(
    "None"              = "grey25", 
    "Geographical"      = "darkgreen",
    "Age/Qualification" = "chocolate4",
    "Age/Qual/FLB"      = "midnightblue"
  )) +
  scale_shape_manual(values = c("None" = "square", "Geographical" = "circle",
        "Age/Qualification" = "circle", "Age/Qual/FLB" = "circle"))

@@

We then calculate the 
proportions of respondents within each sibling group size, based on the respondent
weights, and use this to create weights for the sibling regressions.

@@

drake::loadd(res_wt_flb_weights)
drake::loadd(res_sex)
res_flb_all <- left_join(
        res_wt_flb_weights, 
        res_sex %>% filter(sex=="Female") %>% select(-subset, -sex), 
        by = "term", 
        suffix = c(".wt", ".nowt")
      ) %>% 
      mutate(prop_estimate = estimate.wt/estimate.nowt)

@@

bind_rows(
        Weighted   = res_wt_flb_weights, 
        Unweighted = res_sex %>% filter(sex == "Female") %>% select(-subset, -sex),
        .id        = "Regression"
      ) %>% 
      standard_ggplot(Regression, n_regs = 66)
```
